Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-29 WSSSPE4_report/WSSSPE4_report.tex
fixing quotes

To investigate best practices for scientific software we brought together a panel of five experts with different perspectives on ``Best Practices for Scientific Software''.
These were: Alice Allen, Editor, Astrophysics Source Code Library, brought an understanding of the difficulties of organizing a community and curating their software.
Mike Croucher from the University of Sheffield and Rob Haines from the University of Manchester who are both Research Software Engineers with decades of experience of writing code for researchers.
Patricia Lago from Vrije Universiteit Amsterdam presented a keynote at the workshop (\S\ref{sec:keynote}) and brought a fresh perspective on software sustainability from the point of view of its impact on society and business.
Finally, Karthik Ram from the Berkeley Institute for Data Science brought his perspective on the practicalities of using scientific software to conduct his research as a data scientist.

@@

The panel rounded up with a final question about "If you wanted to have the most disastrous effect on scientific software, what one practice would you advise people to keep doing?"
A few good responses were discussed, but the biggest laugh went to Mike Croucher who said "Containerize everything!"

>>>>

To investigate best practices for scientific software we brought together a panel of five experts with different perspectives on ``Best Practices for Scientific Software.''
These were: Alice Allen, Editor, Astrophysics Source Code Library, brought an understanding of the difficulties of organizing a community and curating their software.
Mike Croucher from the University of Sheffield and Rob Haines from the University of Manchester who are both Research Software Engineers with decades of experience of writing code for researchers.
Patricia Lago from Vrije Universiteit Amsterdam presented a keynote at the workshop (\S\ref{sec:keynote}) and brought a fresh perspective on software sustainability from the point of view of its impact on society and business.
Finally, Karthik Ram from the Berkeley Institute for Data Science brought his perspective on the practicalities of using scientific software to conduct his research as a data scientist.

@@

The panel rounded up with a final question about ``If you wanted to have the most disastrous effect on scientific software, what one practice would you advise people to keep doing?''
A few good responses were discussed, but the biggest laugh went to Mike Croucher who said ``Containerize everything!''
